### 2014-12-03 fundamentals/examples.tex
fixes figure label issue
capitalizes f
tiny changes

The success of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and the feasibility the
 community-driven \Cyclus development model.
Nascent promising growth of the \Cyclus 
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant achievement by the \Cyclus framework 
and provide hope for a community-driven development model.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed which improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.  These tools are used to ease development
and simulation design (Cystub, Cycic, Ciclus), data visualization and analysis (Cyclist, Cyan),
and remote execution (Cloudlus).

@@

Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, and storage
facilities, and expanded institutional paradigms.  These contributed archetypes
illustrate the power of a community-based development approach.

@@

Because material is tracked as discrete objects, single-pass \gls{MOX} 
recycle is easy to implement in \Cyclus.  The MOX simulation includes one provider of fresh
\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.

%** full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
%the scenario described above (all just a single reactor).  **

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources, delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
simulation, the
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was also used, which mixes fissile 
and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\label{fig:flowmodopen}
\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the spent \gls{MOX} fuel of the \Class{BatchReactor}, 
requiring only a one-word change in the input file:

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}

This results in new the material flows in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, 
multi-pass
recycle case.

\begin{figure}[H]
\label{fig:flowclosed}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch worth of
fissile material.

@@

\begin{figure}[H]
\label{fig:puseries1}
\caption{System plutonium buildup with one reactor.}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

The open, modified open, and closed scenarios can easily be modified to have
several reactors each with staggered refueling times. The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}. As the number of
reactors increases, the behavior of the system approaches a more steady
average reminiscent of continuous material flow models.

\begin{figure}[H]
\label{fig:puseriesn}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}

>>>>

The functionality of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and the feasibility the
 community-driven \Cyclus development model.
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-driven \textbf{collaborative?} development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilites. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant achievement by the \Cyclus framework 
and provide the basis for a community-driven development model.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed to improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.  These tools are used to ease development
and simulation design (Cystub, Cycic, Ciclus), data visualization and analysis (Cyclist, Cyan),
and remote execution (Cloudlus).

@@

Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, storage
facilities, and expanded institutional paradigms.  These contributed archetypes
illustrate the power of a community-based development approach.

@@

Because material is tracked as discrete objects, single-pass recycle using \gls{MOX} 
fuel is easy to implement in \Cyclus.  The \gls{MOX} simulation includes one provider of fresh
\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.

%** full-system plutonium buildup for open
\TODO{(no recycle), modified open, and closed (infinite-pass recycle)
variations of}
%the scenario described above (all just a single reactor).  **

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources, delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange \TODO{acro or not?} enables a reactor to
preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
simulation, the
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
source of fresh, enriched uranium and a repository, respectively. A simple
custom recycled fuel fabrication facility was also used, which mixes fissile 
and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in Figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
\label{fig:flowmodopen}
\end{figure}

Changing this to a fully closed fuel cycle entails only a one-word change in the input file
regarding the output commodity for the spent \gls{MOX} fuel of the
\Class{BatchReactor}:

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}
This results in the material flows in Figure \ref{fig:flowclosed}. Note
that the \Class{BatchReactor} always transmutes fuel into the same
composition, so the nuclide level flows are unrealistic for the full, 
multi-pass
recycle case.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
the diff btw closed and the multi-pass from above? It's referred to as fully
closed multi-pass recycle, which is a bit confusing.} variations of
the scenario described above (all just a single reactor).  The figure was
generated directly from \Cyclus output data. After several batch cycles (near
month 300 \TODO{here and below: month or time step?}) in the modified open and closed cases, enough separated fissile
material accumulates in the fuel fabrication facility to generate a full
recycled batch.  When this batch is transmuted, more plutonium is burned than
created.  This results in a drop in the total fuel cycle system plutonium
inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
modified open case and every 9 cycles (180 months) for the closed case.
Because the modified open scenario does not re-recycle material, it takes the
fabrication facility 1 cycle longer to accumulate a full batch of
fissile material.

@@

\begin{figure}[H]
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

The open, modified open, and closed scenarios can easily be modified to have
several reactors with staggered refueling times. The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}. As the number of
reactors increases, the behavior of the system approaches a more steady
average reminiscent of continuous material flow models.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}

### 2014-12-03 fundamentals/intro.tex
tiny changes

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

>>>>

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of modeling and calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precurser,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
at \gls{LDRD} within \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.
